---
title: My wonderful talk
author: Rob J Hyndman
date: last-modified
date-format: D MMMM YYYY
pdf-engine: latexmk
fig-width: 9
fig-height: 4.5
format:
  beamer:
    theme: monash
    aspectratio: 169
    fontsize: 14pt
    section-titles: true
    knitr:
      opts_chunk:
        dev: "CairoPDF"
include-in-header: header.tex
keep-tex: false
toc: false
highlight-style: tango
execute:
  echo: false
  message: false
  warning: false
  cache: true
---

```{r}
#| label: setup
#| cache: false
source(here::here("setup.R"))
```


## Outline

\vspace*{0.7cm}\tableofcontents

# Section 1

## Slide 1
\fontsize{10}{10}\sf

```{r}
#| echo: true
library(fpp3)
pedestrian
```

## Slide 2

Blah blah

```{r}
#| fig-height: 4
pedestrian |>
	fill_gaps(Count = 0) |>
	filter(Sensor == "Southern Cross Station") |>
	gg_season(Count, period = "week")
```

## More information
\fontsize{18}{20}\sf

\href{https://robjhyndman.com/xxx}{\includegraphics[width=0.5cm]{figs/slide}\, robjhyndman.com/xxx}

\href{https://robjhyndman.com}{\faicon{home} robjhyndman.com}

\href{https://twitter.com/robjhyndman}{\faicon{twitter} @robjhyndman}

\href{https://aus.social/@robjhyndman}{\includegraphics[width=0.5cm]{figs/mastodon}\, aus.social/@robjhyndman}

\href{https://github.com/robjhyndman}{\faicon{github}  @robjhyndman}

\href{mailto:rob.hyndman@monash.edu}{\faicon{envelope}  rob.hyndman@monash.edu}

\begin{textblock}{6.2}(0,8.8)\pgfsetfillopacity{0.65}
\begin{beamercolorbox}[wd=4.7cm]{block body}
\fontsize{6}{6}\sf\color[RGB]{72,45,34}\href{https://www.flaticon.com/free-icons/presentation}{Presentation icon created by orvipixel - Flaticon}
\end{beamercolorbox}
\end{textblock}
